---
title: "rct3 Manual"
output: 
  html_document:
    number_sections: TRUE
    df_print: paged
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
vignette: >
  %\VignetteIndexEntry{manual}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  cache=FALSE, cache.path='cache/',
  fig.path  ='tex/man-',
  fig.align='center', comment=NA,
  message=FALSE, warning=FALSE, echo=TRUE,
  fig.width=6, fig.height=4.5)
```


# Description

```{r}
library(rct3)
data(pok)
head(pok)
```

```{r}
fmla <- formula(age4 ~ ibtsq3)

res <- rct3(formula = fmla, data = pok, min.se = 0,
  range = nrow(pok)-1, old = FALSE, shrink = FALSE, power = 0)

summary(res)
```


# plot resulting prediction
```{r}
plot(log(age4) ~ log(ibtsq3), pok, t = "p", pch = 20, col = 8)
pred <- res$rct3.summary

reg <- res$rct3$`yearclass:2015`
# mean observed value
abline(h = reg$prediction[2], col = 8, lty = 2) 
# fitted regression and predicted value
abline(a = reg$intercept[1], b = reg$slope[1], col = 1, lty = 2) 
points(reg$indices[1], pred$logWAP, pch = 20, col = 1)
# assumed value
points(reg$indices[1], log(81298))
legend("topleft", legend = c("Mean", "rct3 pred."), 
  lty = c(2,2), col = c(8,1), pch = c(NA, 20), bty = "n")
```




# References

Shepherd, J.G., 1997. Prediction of year-class strength by calibration regression analysis of multiple recruit index series. ICES Journal of Marine Science: Journal du Conseil 54, 741–752.


# More information

* You can submit bug reports, questions or suggestions on this tutorial at <https://github.com/ices-tools-prod/rct3/issues>.
* Alternatively, send a pull request to <https://github.com/ices-tools-prod/rct3>.


## Software Versions

* `r version$version.string`
* rct3: `r packageVersion('rct3')`
* **Compiled**: `r format(Sys.Date(), '%Y-%b-%d')`


## License

This document is licensed under the [GNU General Public License v2.0](https://www.gnu.org/licenses/old-licenses/gpl-2.0.en.html) license.



